\begin{center}
\begin{longtabu} to \textwidth {|
    X[3,l]|
    X[2,c]|
    X[8,l]|}
    \hline
    \textbf{Author} & \textbf{Date} & \textbf{Message} \\ \hline
Alexander Cherednichenko & 2016-01-20 & Initial commit \\ \hline
Oleksandr Cherednychenko & 2016-01-21 & Adding reports structure, ignores and some seeds for READMEs \\ \hline
E A. Davison & 2016-01-22 & Basic LaTEX files and preamble \\ \hline
Oleksandr Cherednychenko & 2016-01-22 & Correcting ignores for LaTeX \\ \hline
dlphi & 2016-01-25 & test by farik \\ \hline
dlphi & 2016-01-26 & changes to readme \\ \hline
Oleksandr Cherednychenko & 2016-01-26 & Adding corrected gitignore for IntelliJ IDEA not to commit project files (we will use gradle or maven for POM) \\ \hline
E A. Davison & 2016-01-26 & Examples of list, enumeration and the 3 basic types of headings for some starting up help. \\ \hline
Oleksandr Cherednychenko & 2016-01-27 & Adding a build system to the branch, with minimalistic Gradle build. We have 2 submodules, and a top-level gradle build. During the build tests are run (JUnit, Mockito for now), and the result is packaged into runnable apps (/bin and /lib substructure with OS-specific scripts). Modified ther README to reflect all these changes. \\ \hline
Oleksandr Cherednychenko & 2016-01-27 & Added fest-assert for quick and fluent assertions. Updated README \\ \hline
E A. Davison & 2016-01-29 & Quick outline with some basic points added for preliminary report with the report requirements copy-pasted for everyone's convenience \\ \hline
Oleksandr Cherednychenko & 2016-01-29 & Expanded the items for the initial report - mostly what is that we plan to go building \\ \hline
dlphi & 2016-01-31 & adding one bullet point \\ \hline
dlphi & 2016-01-31 & Merge remote-tracking branch 'origin/master' \\ \hline
Inspiron17R & 2016-01-31 & Simulation engine introduction \\ \hline
E A. Davison & 2016-02-01 & Log module (basic) preliminary commit \\ \hline
E A. Davison & 2016-02-01 & Added *.class to the ignore list \\ \hline
E A. Davison & 2016-02-01 & Deleted <Log-Formatter> as functionality migrated to Output specific formatters \\ \hline
Oleksandr Cherednychenko & 2016-02-01 & Removing obsolete settings.gradle from both the subprojects. \\ \hline
Oleksandr Cherednychenko & 2016-02-01 & Adding structure for Es's log module, with dependencies \\ \hline
E A. Davison & 2016-02-01 & PlantUML file for the Class Diagram of the logging system (not complete) \\ \hline
E A. Davison & 2016-02-01 & v.light editing on report \\ \hline
Oleksandr Cherednychenko & 2016-02-01 & Adding basic class diagram to start talking about simulation \\ \hline
E A. Davison & 2016-02-01 & Some re-aranging in the Logger uml diagram \\ \hline
Inspiron17R & 2016-02-02 & Engine report -> technology view \\ \hline
Inspiron17R & 2016-02-02 & Initial report --> Engine's paragraph bibliography \\ \hline
E A. Davison & 2016-02-02 & Added FileIO class to Logger and updated UML class diag. to reflect that \\ \hline
Oleksandr Cherednychenko & 2016-02-02 & Merge branch 'master' into build-system \\ \hline
Oleksandr Cherednychenko & 2016-02-02 & Merge branch 'master' into build-system \\ \hline
Oleksandr Cherednychenko & 2016-02-02 & Moving log files into the new build structure according to packages. \\ \hline
dlphi & 2016-02-02 & Merge remote-tracking branch 'origin/master' \\ \hline
Oleksandr Cherednychenko & 2016-02-02 & Updating readme on how to get the project up and running. \\ \hline
Oleksandr Cherednychenko & 2016-02-02 & Fixing readme formatting \\ \hline
E A. Davison & 2016-02-02 & Moved Logger uml diagram files \\ \hline
E A. Davison & 2016-02-02 & Report: stuff done in group session \\ \hline
Oleksandr Cherednychenko & 2016-02-03 & Expanded 2nd part of the initial report: the process. \\ \hline
Oleksandr Cherednychenko & 2016-02-03 & Added overall architecture diagram \\ \hline
E A. Davison & 2016-02-03 & 1st part of initial report \\ \hline
E A. Davison & 2016-02-03 & Merge branch 'master' of https://github.com/teamIndexZero/index-zero-trafficsystem \\ \hline
E A. Davison & 2016-02-03 & report architecture diagram added to figs \\ \hline
E A. Davison & 2016-02-03 & renamed package to convention (lowercase) \\ \hline
Oleksandr Cherednychenko & 2016-02-03 & Finished initial part 2 of the report. \\ \hline
E A. Davison & 2016-02-03 & log.fileIO.FileIO class implemented + uml diagram updated \\ \hline
E A. Davison & 2016-02-03 & Light editing on preliminary project report (some wording and spacing) \\ \hline
E A. Davison & 2016-02-04 & Group edits on intermediate report \\ \hline
kumar awijeet & 2016-02-04 & PPT for intial report \\ \hline
E A. Davison & 2016-02-04 & log.fileio.FileIO decomposition into FileIO and FileInput/FileOutput classes \\ \hline
E A. Davison & 2016-02-04 & Merge branch 'master' of https://github.com/teamIndexZero/index-zero-trafficsystem \\ \hline
E A. Davison & 2016-02-06 & Debugging, added Output-TXT functionalities, added a MicroLogger for lightweight logging functionality for the Log module (avoids infinite loop/stack overflow when Logger is used on itself) \\ \hline
E A. Davison & 2016-02-07 & Added toString method to Log-TimeStamp \\ \hline
E A. Davison & 2016-02-07 & Added javadoc descriptions to MicroLogger class \\ \hline
kumar awijeet & 2016-02-07 & PPT for initial report \\ \hline
E A. Davison & 2016-02-07 & Log-TimeStamp bug where test would sometimes fail during certain periods of the day squashed (hopefully). \\ \hline
E A. Davison & 2016-02-07 & Added preliminary log-Exception( Exception e ) interface and functionality to Logger \\ \hline
Oleksandr Cherednychenko & 2016-02-07 & Added jacoco for coverage. Fixed global scope for the jUnit - we now can test on top-level module. \\ \hline
E A. Davison & 2016-02-07 & Updated Gradle options to include the Jacoco test coverage plug-in \\ \hline
E A. Davison & 2016-02-07 & Merge branch 'master' of https://github.com/teamIndexZero/index-zero-trafficsystem \\ \hline
E A. Davison & 2016-02-07 & Output and Formatter for the CSV implemented \\ \hline
Oleksandr Cherednychenko & 2016-02-07 & Added more ignores for logs \\ \hline
E A. Davison & 2016-02-07 & Some clean up of the Log-Config and beginning of implementation for the log configuration file loader/checker \\ \hline
E A. Davison & 2016-02-07 & Cleanup of FileInput's exceptions (now sending to MicroLogger), added the message number to exception all outputs/formatters so now shows properly, \\ \hline
Oleksandr Cherednychenko & 2016-02-07 & Added initial run of the simulation. Very basic, boolean 2-dimension array as a base for cell automata map, collection of objects, simplisic rendering. \\ \hline
kumar awijeet & 2016-02-08 & Updated PPT for initial report \\ \hline
E A. Davison & 2016-02-08 & Formatter-TXT and Formatter-TERM unit tests added \\ \hline
E A. Davison & 2016-02-08 & fileIO.Output unit test created \\ \hline
dlphi & 2016-02-08 & Merge remote-tracking branch 'origin/master' \\ \hline
E A. Davison & 2016-02-09 & Added clearFileContent() in log.fileIO.FileOutput, work done on implementation of the config loader in log.Log-Config \\ \hline
E A. Davison & 2016-02-09 & Added variable option (for the log level for now) to the default config writer and the matching regex to the checker \\ \hline
kumar awijeet & 2016-02-09 & PPT for initial report \\ \hline
Oleksandr Cherednychenko & 2016-02-09 & Improved simulation and a bit of gui. We now have colors for objects. Redone rendering - now instead of bitmap from map[] thing we have objects drawn one by one. \\ \hline
E. A. Davison & 2016-02-09 & Bug squashed in log.fileIO.FileOutput where when clearing the file it would leave the state closed, log.Log-Config file loader for the config implemented \\ \hline
E. A. Davison & 2016-02-09 & Fixed typo in OutputTest \\ \hline
E. A. Davison & 2016-02-09 & Squashed bug that kept defaulting to default file name output for logs despite names being different in the config file, added a timestamp extension to all file outputs, added more examples to the default log-config file \\ \hline
dlphi & 2016-02-09 & Merge remote-tracking branch 'origin/master' \\ \hline
kumar awijeet & 2016-02-10 & Replacing old file - orignal method not working. Trying another process. \\ \hline
kumar awijeet & 2016-02-10 & Final PPT files for intial report \\ \hline
E. A. Davison & 2016-02-11 & Final report headings added and section info from the guidelines added in as comments \\ \hline
Oleksandr Cherednychenko & 2016-02-11 & Added readme quick notes on Running the software. Ignored log-config.cfg \\ \hline
Oleksandr Cherednychenko & 2016-02-11 & Merge remote-tracking branch 'origin/master' \\ \hline
Oleksandr Cherednychenko & 2016-02-12 & Merge remote-tracking branch 'origin/farik' \\ \hline
E. A. Davison & 2016-02-12 & Activity diag for the basic demo added, folder for uml stuff created and all other uml diag migrated to it. \\ \hline
E. A. Davison & 2016-02-12 & Changed default log level to "WARNING" to keep logging light by default for performance (disk IO) -> if level need to be changed do it in the log-config.cfg file from now on. \\ \hline
Oleksandr Cherednychenko & 2016-02-12 & 1 of 2 Simulator Improvements - added quite a lot of comments mostly. \\ \hline
dlphi & 2016-02-12 & Merge remote-tracking branch 'origin/master' \\ \hline
Oleksandr Cherednychenko & 2016-02-12 & 2 of 2 Simulator improvements - added comments where appropriate \\ \hline
Oleksandr Cherednychenko & 2016-02-12 & Merge remote-tracking branch 'origin/master' into simulatorImprovements \\ \hline
Oleksandr Cherednychenko & 2016-02-12 & Merge. \\ \hline
Oleksandr Cherednychenko & 2016-02-12 & Updated class diagram to the actual state \\ \hline
Oleksandr Cherednychenko & 2016-02-12 & Updated class diagram to the actual state \\ \hline
E. A. Davison & 2016-02-12 & Cleaned out code in Log-Config: simplified loadConfiguration(..), applyConfigurationLine(..) now return boolean \\ \hline
Alexander Cherednichenko & 2016-02-12 & Merge pull request -2 from teamIndexZero/logImprovements \\ \hline
Es & 2016-02-12 & Merge pull request -1 from teamIndexZero/simulatorImprovements \\ \hline
Inspiron17R & 2016-02-13 & CrossRoads--> class first version, architecture. \\ \hline
Oleksandr Cherednychenko & 2016-02-13 & Emergency fix - commented out @Jacek's code which is breaking the build so that others can build master branch. \\ \hline
E. A. Davison & 2016-02-13 & log.Logger unit test (with mockito) \\ \hline
E. A. Davison & 2016-02-13 & Merge branch 'master' of https://github.com/teamIndexZero/index-zero-trafficsystem into logImprovements \\ \hline
Oleksandr Cherednychenko & 2016-02-13 & Added some basic tests for simulator - mostly making sure it runs the ISimulationAware instances in correct order. \\ \hline
Oleksandr Cherednychenko & 2016-02-13 & Trying to trigger travis build with this commit - amending the pull request. \\ \hline
Oleksandr Cherednychenko & 2016-02-13 & Adding travis build server description file \\ \hline
Oleksandr Cherednychenko & 2016-02-13 & Trying to force Travis to use jdk 8 (and language level 8) \\ \hline
Oleksandr Cherednychenko & 2016-02-13 & Fixing weird case bug - IDEA does not recognize file is in lower case \\ \hline
Oleksandr Cherednychenko & 2016-02-13 & Merge branch 'master' into simulatorImprovements \\ \hline
Inspiron17R & 2016-02-13 & CrossRoads-->adding mechanical and automatic lights. \\ \hline
Inspiron17R & 2016-02-13 & CrossRoads-->adding mechanical and automatic lights. \\ \hline
Inspiron17R & 2016-02-13 & Merge remote-tracking branch 'origin/master' \\ \hline
Inspiron17R & 2016-02-13 & CrossRoads-->adding mechanical and automatic lights. \\ \hline
Inspiron17R & 2016-02-14 & Vehicle2 --> temporary class. CrossRoads-->linking with Vehicle 2. \\ \hline
E. A. Davison & 2016-02-14 & Merge branch 'master' of https://github.com/teamIndexZero/index-zero-trafficsystem into logImprovements \\ \hline
dlphi & 2016-02-14 & Merge remote-tracking branch 'origin/master' \\ \hline
dlphi & 2016-02-14 & adding serialization (writing) to main method \\ \hline
dlphi & 2016-02-14 & adding Serializable \\ \hline
dlphi & 2016-02-14 & adding deserialization \\ \hline
Inspiron17R & 2016-02-15 & CrossRoads-->improvements. \\ \hline
E. A. Davison & 2016-02-15 & Merge branch 'simulatorImprovements' of https://github.com/teamIndexZero/index-zero-trafficsystem into logImprovements \\ \hline
E. A. Davison & 2016-02-15 & Merge branch 'serialization' of https://github.com/teamIndexZero/index-zero-trafficsystem into logImprovements \\ \hline
E. A. Davison & 2016-02-15 & Merge branch 'master' of https://github.com/teamIndexZero/index-zero-trafficsystem into logImprovements \\ \hline
E. A. Davison & 2016-02-15 & Small tweak in main classes to make them more testable + depreciation of unused method(s) in Log-Engine \\ \hline
Inspiron17R & 2016-02-16 & Straight cars movement on the crossroad. \\ \hline
E. A. Davison & 2016-02-16 & Merge branch 'master' of https://github.com/teamIndexZero/index-zero-trafficsystem into logImprovements \\ \hline
E. A. Davison & 2016-02-17 & Log-Engine unit tests implemented \\ \hline
E. A. Davison & 2016-02-17 & Log-Engine unit test implemented \\ \hline
E. A. Davison & 2016-02-17 & Log-Config unit tests implemented \\ \hline
E. A. Davison & 2016-02-17 & Output-TERM unit tests implemented \\ \hline
dlphi & 2016-02-17 & Merge remote-tracking branch 'origin/master' \\ \hline
Es & 2016-02-17 & Merge pull request -3 from teamIndexZero/simulatorImprovements \\ \hline
Oleksandr Cherednychenko & 2016-02-17 & Pusing the new branch for movement, features and traffic lights. \\ \hline
dlphi & 2016-02-17 & some bullet points \\ \hline
dlphi & 2016-02-17 & Merge remote-tracking branch 'origin/master' \\ \hline
Oleksandr Cherednychenko & 2016-02-17 & Merge remote-tracking branch 'origin/master' into graphAndMovement \\ \hline
E. A. Davison & 2016-02-17 & Output-TXT unit tests implemented + some changes to FileIO/FileOutput and Output-TXT to ease testing \\ \hline
E. A. Davison & 2016-02-17 & FileIO unit tests implemented + minor corrections to Log code \\ \hline
E. A. Davison & 2016-02-17 & Revert "Merge branch 'serialization' of https://github.com/teamIndexZero/index-zero-trafficsystem into logImprovements" \\ \hline
E. A. Davison & 2016-02-17 & Unit test fail repairs (1/2) \\ \hline
E. A. Davison & 2016-02-17 & Unit test fail repairs (2/2) \\ \hline
E. A. Davison & 2016-02-17 & Formatter-CSV unit tests implementation (1/2) \\ \hline
E. A. Davison & 2016-02-18 & File-Output unit tests partly implemented.. (not fully successful) \\ \hline
E. A. Davison & 2016-02-19 & Deleted useless section of the Log-Config.getGlobalLevel() unti test \\ \hline
Oleksandr Cherednychenko & 2016-02-20 & Ignoring the test with missing functionality - it is described in TODO \\ \hline
Oleksandr Cherednychenko & 2016-02-21 & Moved things into corresponding packages. Added threading support to Simulator. Added toolbar to main window. \\ \hline
E. A. Davison & 2016-02-21 & File-Output unit tests implemented - working \\ \hline
Oleksandr Cherednychenko & 2016-02-21 & Merge branch 'master' into logImprovements \\ \hline
Alexander Cherednichenko & 2016-02-21 & Merge pull request -4 from teamIndexZero/logImprovements \\ \hline
E. A. Davison & 2016-02-21 & File-Input unit tests implemented + some added funct. to ease testing \\ \hline
E. A. Davison & 2016-02-21 & Merge remote-tracking branch 'origin/logImprovements' into logImprovements \\ \hline
E. A. Davison & 2016-02-21 & Beautification of msg number for TERM and TXT output + tests updated \\ \hline
E. A. Davison & 2016-02-21 & Output-CSV and Formatter-CSV with their test done + some minor corrections \\ \hline
Oleksandr Cherednychenko & 2016-02-21 & Addel GuiModel::Reset and proper painting lifeecycle for the map panel component. \\ \hline
Oleksandr Cherednychenko & 2016-02-21 & Getting coordinates to order \\ \hline
Oleksandr Cherednychenko & 2016-02-21 & Merge remote-tracking branch 'origin/master' into backgroundThread \\ \hline
Alexander Cherednichenko & 2016-02-21 & Merge pull request -5 from teamIndexZero/logImprovements \\ \hline
Oleksandr Cherednychenko & 2016-02-21 & Merge remote-tracking branch 'origin/master' into backgroundThread \\ \hline
Oleksandr Cherednychenko & 2016-02-22 & Added UML diagram for threading and MVC. \\ \hline
Oleksandr Cherednychenko & 2016-02-22 & Added tests for GUI controller Added commentaries to the code. \\ \hline
Oleksandr Cherednychenko & 2016-02-22 & Reformatting code and optimizing imports. \\ \hline
E. A. Davison & 2016-02-24 & File-Input/File-Output .close* updated with raising exception when failing instead of boolean \\ \hline
Inspiron17R & 2016-02-24 & Merge remote-tracking branch 'origin/master' into graphAndMovement \\ \hline
E. A. Davison & 2016-02-24 & Formatter-CSV - any ';' replaced with '¬' before csv formatting to avoid extra unwanted cols in output. Unit test updated with this in mind. \\ \hline
Alexander Cherednichenko & 2016-02-24 & Merge pull request -6 from teamIndexZero/logImprovements \\ \hline
Oleksandr Cherednychenko & 2016-02-24 & Merge remote-tracking branch 'origin/master' into backgroundThread \\ \hline
Oleksandr Cherednychenko & 2016-02-24 & Fixing the reset test. \\ \hline
Es & 2016-02-24 & Merge pull request -7 from teamIndexZero/backgroundThread \\ \hline
Oleksandr Cherednychenko & 2016-02-25 & Merge branch 'master' into graphAndMovement \\ \hline
Oleksandr Cherednychenko & 2016-02-25 & Resolving textual conflicts after the changes were merged in. \\ \hline
Inspiron17R & 2016-02-26 & Merge branch 'graphAndMovement' of https://github.com/teamIndexZero/index-zero-trafficsystem into graphAndMovement \\ \hline
Inspiron17R & 2016-02-27 & Movement improvements. \\ \hline
Inspiron17R & 2016-02-27 & Movement improvements adding lines class. \\ \hline
E. A. Davison & 2016-02-27 & Graph creation beginnings... (+fresh start of the features/links for e-z preliminary testing) \\ \hline
E. A. Davison & 2016-02-27 & ongoing work save... resuming tomorrow \\ \hline
E. A. Davison & 2016-02-28 & SimulationMap modified to enable feature/link injection through constructor \\ \hline
E. A. Davison & 2016-02-28 & Final Report update (some Log module stuff and mention of OSM and SUMO (<-need expansion) ) \\ \hline
E. A. Davison & 2016-02-28 & Save point (work in progress) \\ \hline
E. A. Davison & 2016-02-28 & Save point (work in progress) \\ \hline
E. A. Davison & 2016-02-28 & Save point (work in progress) \\ \hline
E. A. Davison & 2016-03-01 & Save point (work in progress) - Feature[Road/DirectedLanes/Lane/RoadSpecs], ID augmented with descriminant constructor, some class moved into their own packages (i.e. cleaning up) \\ \hline
E. A. Davison & 2016-03-01 & Unit Tests for: DirectedLanes, Lane, ID + small mods to squash found bugs \\ \hline
E. A. Davison & 2016-03-01 & Unit Test: Road + some changes to the class to add getLeftLaneCount and getRightLaneCount methods \\ \hline
E. A. Davison & 2016-03-01 & Save point (work in progress) - GraphConstructor created to move that concern out of the SimulationMap. LinkDescription added for carrying description of the logical connections inside the graph to the GraphConstructor. \\ \hline
E. A. Davison & 2016-03-01 & Save point (work in progress) - More work on the GraphConstructor, added ID for the LinkDescription class and a LinkType class. \\ \hline
E. A. Davison & 2016-03-01 & Save point (work in progress) - LinkDescription.toString() added + its Unit Test \\ \hline
E. A. Davison & 2016-03-01 & Save point (work in progress) - GraphConstructor.createGraph() now can deal with features that end abruptly. \\ \hline
E. A. Davison & 2016-03-01 & Save point (work in progress) - Link.isDeadEnd() method added \\ \hline
E. A. Davison & 2016-03-02 & Save point (work in progress) - GraphConstructor.addLink(..) done, MissingImplementationException class added for missing switch cases in the code, Basic traffic light classes added. \\ \hline
E. A. Davison & 2016-03-02 & Save point (work in progress) - Traffic light classes arranged, Road descriptor added \\ \hline
E. A. Davison & 2016-03-02 & Save point (work in progress) - TrafficLightRule \\ \hline
E. A. Davison & 2016-03-02 & simulator object diagram outline (not complete) \\ \hline
E. A. Davison & 2016-03-02 & simulator object diagram outline (not complete) edit. \\ \hline
E. A. Davison & 2016-03-02 & Save point \\ \hline
Oleksandr Cherednychenko & 2016-03-02 & Fixing the graph buildup (original) in order to carry on with coordinate system conversion. \\ \hline
E. A. Davison & 2016-03-02 & RoadLink (composed of Link(s)) added for linking macro Features like Road - Junction \\ \hline
Oleksandr Cherednychenko & 2016-03-03 & Added OSM loader (from XML). Added three sample OSM files - for Strand, El'n'castle, and for Buckingham palace area. Added a preliminary UI component - the app starts with the initial small screen where user can select their map (one of pre-set for now). Added proper coordinate conversion between lat/lon within the bounding box, and on-screen coordinate (for now it SCALES!) \\ \hline
Oleksandr Cherednychenko & 2016-03-03 & Minor fix for the interface. \\ \hline
Oleksandr Cherednychenko & 2016-03-03 & Refactoring window out to the extra class to make it a bit more readable. Decoupling the window size through model (no direct dependency between panel and imageproducer now). \\ \hline
E. A. Davison & 2016-03-04 & Work on the descriptors (added JunctionDescriptor class as place holder) \\ \hline
E. A. Davison & 2016-03-04 & Removed redundant comments \\ \hline
Oleksandr Cherednychenko & 2016-03-04 & Added coordinate conversion latlon -> geo Added UI for map list. Added UI for settings Added highlighting of the moving car. Added car details panel. Tweaked traffic generator. Tweaked traffic remover. Polyline roads - now, the road is represented by geo polyline, and movement happens along it. \\ \hline
Oleksandr Cherednychenko & 2016-03-04 & Merge remote-tracking branch 'origin/graphCreation' into graphCreation \\ \hline
Oleksandr Cherednychenko & 2016-03-04 & Committing details for graph creation w/Es. \\ \hline
E. A. Davison & 2016-03-04 & JunctionDescription class getters and docs added \\ \hline
E. A. Davison & 2016-03-04 & Some refactoring and docs added to RoadDescription and Road classes \\ \hline
E. A. Davison & 2016-03-04 & LinkDescription unit test added \\ \hline
E. A. Davison & 2016-03-04 & RoadDescription unit test added \\ \hline
E. A. Davison & 2016-03-04 & JunctionDescription unit tests added \\ \hline
E. A. Davison & 2016-03-04 & RoadTest updated with refactor \\ \hline
Oleksandr Cherednychenko & 2016-03-04 & Fixing aspect ratio issue (now we are properly rectilinear). Renaming lat and lon to x and y where it should be x and y. \\ \hline
E. A. Davison & 2016-03-05 & TrafficQuota class added with unit test \\ \hline
E. A. Davison & 2016-03-05 & Updated exceptions for chaining \\ \hline
E. A. Davison & 2016-03-05 & JunctionPathException added \\ \hline
E. A. Davison & 2016-03-05 & TrafficQuota.toString() added \\ \hline
E. A. Davison & 2016-03-05 & TrafficBehaviour + unit test added \\ \hline
E. A. Davison & 2016-03-05 & Vehicle constructor added to be able to pass Lanes instead \\ \hline
E. A. Davison & 2016-03-05 & Lane.getRoadID() and Lane.getParentRoad() added \\ \hline
E. A. Davison & 2016-03-05 & TrafficGenerator feature added (functionality copied/adapted from Alex's CarAdder) \\ \hline
E. A. Davison & 2016-03-05 & added the new Lane methods into the unit test \\ \hline
E. A. Davison & 2016-03-05 & Refactoring following correcting the spelling mistake for the name of the 'exception' package (from 'exeption') \\ \hline
E. A. Davison & 2016-03-05 & new png files for the uml. Nothing important \\ \hline
E. A. Davison & 2016-03-05 & Small changes (space, method call signature and such). nothing important. \\ \hline
Oleksandr Cherednychenko & 2016-03-06 & Altering interface of JunctionDescription - we now have way to pass road direction relative to the junction. \\ \hline
E. A. Davison & 2016-03-06 & Merge remote-tracking branch 'origin/graphCreation' into graphCreation \\ \hline
E. A. Davison & 2016-03-06 & TrafficBehaviour update with method to get all exit link IDs for a inflow link to bypass behaviour control (inc. update to unit test) \\ \hline
E. A. Davison & 2016-03-06 & HashCode + Equals override for Link added \\ \hline
E. A. Davison & 2016-03-06 & RoadLink class deleted, little to no use so refactored \\ \hline
E. A. Davison & 2016-03-06 & JunctionDesc. doc and import cleaned up \\ \hline
E. A. Davison & 2016-03-06 & ID: new constructor added for placing a discriminant in front of tag + some doc updates \\ \hline
E. A. Davison & 2016-03-06 & Road refactored and unit test updated with for new methods \\ \hline
E. A. Davison & 2016-03-06 & Lane refactored + unit test updated \\ \hline
E. A. Davison & 2016-03-06 & JunctionLink class + unit test (part 2) \\ \hline
E. A. Davison & 2016-03-06 & JunctionLink.getNextFeature() added (+ test) \\ \hline
E. A. Davison & 2016-03-06 & Lane.getNextLink() added (+ test) \\ \hline
E. A. Davison & 2016-03-06 & Log docs cleaned up \\ \hline
E. A. Davison & 2016-03-06 & Little bit of refactoring - nothing major \\ \hline
E. A. Davison & 2016-03-06 & JunctionLink test updated \\ \hline
E. A. Davison & 2016-03-06 & Junction class implemented + unit test \\ \hline
E. A. Davison & 2016-03-06 & TrafficGenerator.getRandomLane() has a cast inside to work with the requirements of the Junction/JunctionLink stuff \\ \hline
Oleksandr Cherednychenko & 2016-03-06 & Commented out some breaking code. Fixed GUI test. \\ \hline
E. A. Davison & 2016-03-07 & -Cleaned up GraphConstructor a for preparation of final stage implementation of its functionality -General small cleanup \\ \hline
E. A. Davison & 2016-03-07 & DirectedLanes docs updated \\ \hline
E. A. Davison & 2016-03-07 & DirectedLanes unit tests upddated \\ \hline
E. A. Davison & 2016-03-07 & GraphConstructor work on linkage \\ \hline
E. A. Davison & 2016-03-08 & Migrated usefull tool methods from GraphConstructor to their own GraphTools class to avoid code duplication \\ \hline
E. A. Davison & 2016-03-08 & Moved createLink() method from GraphConstructor to GraphTools GraphGenerator.addTrafficGenerators() implemented, TrafficGenerator.linkRoad() implemented \\ \hline
E. A. Davison & 2016-03-08 & TrafficBehaviour.getNextDestinationLinkID() doc set to depreciated since we're going to let the vehicles decide from a list where to go at junctions (TrafficBehaviour.getAllPossibleExitPoints(..)) \\ \hline
E. A. Davison & 2016-03-08 & GraphTools unit test + slight corrections \\ \hline
E. A. Davison & 2016-03-08 & More TrafficGenerator work done (in progress) \\ \hline
Oleksandr Cherednychenko & 2016-03-08 & Changed UI icons. Finalized coordinate system conversion. Refactored Viewport model out of GuiModel. Added mouse events for the map panel: pan/zoom/move. Added zoom reset button to the toolbar. Now stop simulation button start the sequence over - from the map chooser. \\ \hline
Inspiron17R & 2016-03-09 & TrafficLights classes first view. \\ \hline
Oleksandr Cherednychenko & 2016-03-09 & Fixed project to be actually buildable. \\ \hline
Oleksandr Cherednychenko & 2016-03-09 & Adding some error handling AND fixing traffic lights NullPointerException \\ \hline
Oleksandr Cherednychenko & 2016-03-09 & Moving files \\ \hline
Oleksandr Cherednychenko & 2016-03-09 & Minor fix - typo. \\ \hline
Inspiron17R & 2016-03-09 & TrafficLights test schema. \\ \hline
Oleksandr Cherednychenko & 2016-03-09 & Renaming capital stuff \\ \hline
Oleksandr Cherednychenko & 2016-03-09 & Added layers support (for multi-level junctions and road layouts) - now we read it from the OSM XML properly. \\ \hline
Oleksandr Cherednychenko & 2016-03-09 & Fixing test (Travis does not have UI) \\ \hline
Alexander Cherednichenko & 2016-03-09 & Merge pull request -8 from teamIndexZero/graphCreation \\ \hline
E. A. Davison & 2016-03-09 & Some Log message \\ \hline
E. A. Davison & 2016-03-09 & TrafficLight patch \\ \hline
E. A. Davison & 2016-03-10 & GraphConstructor Unit Test setup \\ \hline
Oleksandr Cherednychenko & 2016-03-10 & Added link and junction collection from OSM XML. \\ \hline
E. A. Davison & 2016-03-10 & GraphConstructor save point \\ \hline
E. A. Davison & 2016-03-10 & GraphConstructor save point \\ \hline
Oleksandr Cherednychenko & 2016-03-10 & Merge remote-tracking branch 'origin/GraphConstruction' into testIntegration \\ \hline
Oleksandr Cherednychenko & 2016-03-11 & Coordinated movement (cars now are able to pass junctions). \\ \hline
E. A. Davison & 2016-03-14 & Alex's log patch applied (problem with object print) and graph integrity function \\ \hline
E. A. Davison & 2016-03-15 & Alex's chicken/egg problem solution with the TrafficGenerators and applying the map \\ \hline
E. A. Davison & 2016-03-15 & Deleting depreciated features, cleaning up code, sorting out the TrafficGenerators \\ \hline
Oleksandr Cherednychenko & 2016-03-15 & Changed packaged OSM files to have complete ways (a must for simulation) Added an option to load file from outside Added debug road flag/setting to show roads in rainbow colors to see where they intersect. improved OSM file post-processing: now, when we spot a road which has a junction in the middle, it splits that road into two (or as many as needed) and connects both. This fixed many issues with 'hanging links.' \\ \hline
Oleksandr Cherednychenko & 2016-03-16 & Cleaned up data files a little (removing orphaned features). Getting rid of old MapPosition. Adding driving behavior for a vehicle (speed and acceleration) \\ \hline
E. A. Davison & 2016-03-16 & Added traffic generator switch to the gui, some cleanup of the log messages \\ \hline
E. A. Davison & 2016-03-16 & Bug where TrafficGenerators are propagating like rabbits on the map squashed \\ \hline
dlphi & 2016-03-16 & more bullet points \\ \hline
dlphi & 2016-03-16 & more bullet points \\ \hline
Oleksandr Cherednychenko & 2016-03-16 & Enabling support for traffic-generator-link in addition to junction link. Removing CarAdder and CarRemover - TrafficGenerators are doing that job now (both sending new cars and receiving old ones to remove. \\ \hline
dlphi & 2016-03-16 & more bullet points \\ \hline
E. A. Davison & 2016-03-17 & TrafficGenerator vehicle receiver/deleted sorted \\ \hline
E. A. Davison & 2016-03-17 & TrafficGenerators now added to all dead ends :) \\ \hline
E. A. Davison & 2016-03-17 & TrafficGenerators can now be added to inflow only junction to provide an outflow path receptor; \\ \hline
E. A. Davison & 2016-03-17 & More work on linkage traversal \\ \hline
E. A. Davison & 2016-03-17 & Cleaned up the last TrafficGenerator functionalities added and got rid of superfluous code in GraphConstructor that was depreciated. \\ \hline
Oleksandr Cherednychenko & 2016-03-18 & - Lane visualization: drawing them separately, correct metric offset, different coloring. - Cars are now able to hold on to physics: when approaching a junction, they will not turn if the angle of the outgoing lane is too small (that is, no 14 degree turns) - Added frame rate optimization to ImageProducer: we limit FPS by 25 - Added static features image caching for ImageProducer: if we don't change viewport or request roads to redraw, they don't. This improves performance dramatically. - Now we are able to select a car by simply clicking it. - Created a separate traffic generator to collect all orphaned cars (not the best thing, but it at least now works well). \\ \hline
Oleksandr Cherednychenko & 2016-03-18 & Added diagrams for the report: data pipeline and different coordinate systems we have. \\ \hline
Oleksandr Cherednychenko & 2016-03-19 & - Selecting a vehicle on map does not lead to background redraw now. - Number of lanes can be decimal in OSM file (wat?), working that around. \\ \hline
E. A. Davison & 2016-03-19 & Sorted out the edge case where only inflow roads where coming into a junction save one and the inflow of that exception could not go anywhere. Now a traffic generator is placed on those junctions. \\ \hline
E. A. Davison & 2016-03-19 & Removed the "all catcher" TrafficGenerator from the code as no longer needed \\ \hline
Oleksandr Cherednychenko & 2016-03-19 & Adding sample data for manhattan and big greater london. \\ \hline
Oleksandr Cherednychenko & 2016-03-19 & Merge remote-tracking branch 'origin/linkAndJunctionsParsingFromOSM' into linkAndJunctionsParsingFromOSM \\ \hline
Oleksandr Cherednychenko & 2016-03-19 & Added one more sample for Manhattan Battery Park \\ \hline
E. A. Davison & 2016-03-19 & Merge remote-tracking branch 'origin/linkAndJunctionsParsingFromOSM' into linkAndJunctionsParsingFromOSM \\ \hline
E. A. Davison & 2016-03-19 & Potential bug squashed where new vehicle out of TrafficGenerator were trying to get a lane but would break when connected to a junction \\ \hline
Oleksandr Cherednychenko & 2016-03-19 & Fixing vehicle movement (on lane) - we only look at what to do after the lane ends. \\ \hline
E. A. Davison & 2016-03-19 & Moved the rendering of the junctions and TF to dynamic in order for the IN/OUT, passthrough data to be displayed accurately \\ \hline
E. A. Davison & 2016-03-19 & TrafficGenerator unit test added \\ \hline
Oleksandr Cherednychenko & 2016-03-20 & Improving vehicle movement - now we observe angles more carefully. UI: the details panel now has fixed width which stops expensive redraws when longest street name changes. Fixing tests. \\ \hline
Oleksandr Cherednychenko & 2016-03-20 & Merge remote-tracking branch 'origin/linkAndJunctionsParsingFromOSM' into linkAndJunctionsParsingFromOSM \\ \hline
E. A. Davison & 2016-03-20 & JunctionTest: missing methods generated \\ \hline
E. A. Davison & 2016-03-20 & slight changes, nothing of note \\ \hline
Oleksandr Cherednychenko & 2016-03-20 & Added a list of the features currently on map. \\ \hline
Oleksandr Cherednychenko & 2016-03-20 & Merge remote-tracking branch 'origin/linkAndJunctionsParsingFromOSM' into linkAndJunctionsParsingFromOSM \\ \hline
Oleksandr Cherednychenko & 2016-03-20 & Added some performance numbers to the report. \\ \hline
Oleksandr Cherednychenko & 2016-03-21 & Added junction debug display, now we can select junction and see its incoming/outgoing lanes with appropriate angles. Using this information, one can understand the mechanics the junction works and how cars switch. \\ \hline
E. A. Davison & 2016-03-21 & Unit test update for new methods that were not added to the tests \\ \hline
E. A. Davison & 2016-03-21 & Bug in timestamp relating to fractions of seconds squashed by changing it to nano. \\ \hline
E. A. Davison & 2016-03-21 & Sorted out breaking test in TrafficGeneratorTest and added missing tests. \\ \hline
E. A. Davison & 2016-03-21 & Remove redundant map factory \\ \hline
E. A. Davison & 2016-03-21 & Increased the number of time the tick is called for the test so that it passes \\ \hline
E. A. Davison & 2016-03-21 & Junction unit tests mostly done \\ \hline
E. A. Davison & 2016-03-21 & Road unit tests all implemented \\ \hline
E. A. Davison & 2016-03-21 & Behaviour unit tests all implemented \\ \hline
E. A. Davison & 2016-03-21 & Removed unused exceptions \\ \hline
E. A. Davison & 2016-03-21 & Cleaned and updated the Junction unit tests \\ \hline
E. A. Davison & 2016-03-21 & typo corrected \\ \hline
E. A. Davison & 2016-03-21 & TODO updated to be more descriptive \\ \hline
Inspiron17R & 2016-03-21 & New bullet points about traffic lights. \\ \hline
E. A. Davison & 2016-03-22 & JunctionLink unit test implemented \\ \hline
E. A. Davison & 2016-03-22 & Link unit tests implemented \\ \hline
E. A. Davison & 2016-03-22 & some light cleanup \\ \hline
Oleksandr Cherednychenko & 2016-03-22 & Added lane changing code. \\ \hline
Alexander Cherednichenko & 2016-03-22 & Merge pull request -11 from teamIndexZero/linkAndJunctionsParsingFromOSM \\ \hline
Oleksandr Cherednychenko & 2016-03-22 & Added notion of width/height for cars (uncovers after some zoom in) \\ \hline
Oleksandr Cherednychenko & 2016-03-22 & Added lane changing code. \\ \hline
Oleksandr Cherednychenko & 2016-03-22 & Added notion of width/height for cars (uncovers after some zoom in) \\ \hline
Oleksandr Cherednychenko & 2016-03-22 & Merge remote-tracking branch 'origin/laneChanging' into laneChanging \\ \hline
Oleksandr Cherednychenko & 2016-03-23 & Fixing tests. \\ \hline
E. A. Davison & 2016-03-23 & Merge remote-tracking branch 'remotes/origin/master' into report \\ \hline
Oleksandr Cherednychenko & 2016-03-23 & Fixing javadocs across the project. \\ \hline
E. A. Davison & 2016-03-23 & resurrected plantUml logger class diag. description \\ \hline
Es & 2016-03-23 & Merge pull request -12 from teamIndexZero/laneChanging \\ \hline
E. A. Davison & 2016-03-23 & - Logger class diag updated - Logger overview object diag created \\ \hline
E. A. Davison & 2016-03-23 & - Added logger object diag to report + fixed compile errors in LaTEX \\ \hline
E. A. Davison & 2016-03-23 & - updated logger object diag. (got rid of title) \\ \hline
E A. Davison & 2016-03-23 & - Added items in Graph, Logger and TF section of report \\ \hline
E. A. Davison & 2016-03-23 & - Report: added pic for roads \\ \hline
Oleksandr Cherednychenko & 2016-03-23 & Added some excerpts illustrating different situations in simualtion. \\ \hline
Oleksandr Cherednychenko & 2016-03-23 & Merge remote-tracking branch 'origin/report' into report \\ \hline
E. A. Davison & 2016-03-23 & - Report update \\ \hline
E. A. Davison & 2016-03-23 & - Trello screen shot \\ \hline
Oleksandr Cherednychenko & 2016-03-23 & Merge branch 'master' into report \\ \hline
E. A. Davison & 2016-03-23 & - Report update (Graph construction) \\ \hline
E. A. Davison & 2016-03-23 & Merge remote-tracking branch 'origin/report' into report \\ \hline
E. A. Davison & 2016-03-23 & - Report update \\ \hline
E. A. Davison & 2016-03-23 & - Report update \\ \hline
Oleksandr Cherednychenko & 2016-03-24 & Added readme for the software package to stay within archive. Added Tech section in report. \\ \hline
Oleksandr Cherednychenko & 2016-03-24 & Added gitlog script and actual git log in TeX format. Elaborated a little more on map construction and rendering details. \\ \hline
Oleksandr Cherednychenko & 2016-03-24 & Updated lane changing images in report. \\ \hline
Oleksandr Cherednychenko & 2016-03-24 & Added listing inclusion generators and actual listing inclusions. Disabled for now as it turns the report into 183-pager. \\ \hline


\end{longtabu}
\end{center}
