%Max 1500w or 4 pages
%Deadline 17:00 on Tuesday 09-02-2016

\section{Introduction}

The project aims to create a micro-modelled road traffic simulation engine enabling inspection of various effects of changing key rules within the model. For team members, this project is centered around teamwork and also, as a less prominent addition, the learning and application of software engineering skills.

\section{Project Description} %~60% of the report
Describe your team’s aims for the projects. Outline what aims your team have set for the project and your strategy for
achieving those aims. A rough timetable may be appropriate and you may wish to break your aims into levels
 (e.g. mandatory / optional or we will first work on level 1 aims before moving to level 2 aims) to allow for
 unexpected issues that may arise. You must also describe how your initial progress developing your piece of software
 has gone and where you currently are relative to your aims.
 

\subsection{Project Outline}


research micro/macro
architecture
division into artifact (gui,simulator,log)




\subsubsection{Model}

As the micro-model implementation focuses on individual representation of cars as physical objects and individual tuning of their parameters the starting point chosen is based on the Nagel–Schreckenberg model. The roads in this model are represented as cellular automata\cite{Schreckenberg}. In this, each cell can either be occupied by an object or be empty. Cars can have different properties such as acceleration, speed, direction and can move to other free neighbouring cells. The model can be expanded through the use of graphs to connect roads.

In the early stages streets will be arranged to model simple road networks and, in time, more realistic ones.
Rules in the simulation will include driving rules such as crossings, lane changes, etc.., and laws of physics. That can be further expanded to include weather factors and engine emissions.

The simulation system will be used to gather relevant data for analysis that can include road network throughput, congestion effects, pollution and more generally reaction of the model to changing rules.

\subsubsection{Technical considerations} %%??


\subsubsection{}

	\begin{itemize}
		\item approach (conceptual and technical)
		\begin{itemize}
		    \item Base: build, test, IDE, rough architecture set up.
		    

		\end{itemize}

		\item rough architecture
		\begin{itemize}
		    \item Component 1 - simulator
		    \item Component 2 - GUI/animation engine
		\end{itemize}

		\item technology choice: Java. Why?:
		\begin{itemize}
		    \item maximum intersection set of what team knows
		    \item many libraries and tools, incl. spatial, modelling, parallelism, etc.
		    \item it is cross-platform, and can run on all 3 major OSs (we have Windows and Mac in team)
		    \item Has GUI capabilities
		\end{itemize}

	\end{itemize}
\subsection{Timetable}
 

\begin{itemize}


	\item Rough plan (estimate). Splitting all 2 months into 4 rough periods:
	\begin{itemize}

	    \item By 9th of Feb - initial report submission time:
	    \begin{itemize}
	        \item Team structure ready
	        \item Team process setup (communication, teamwork, knowledge sharing, visibility)
	        \item Rough architecture outlined, some basics set for modelling
	    \end{itemize}

	    \item by March 1st - less than 1 month iteration
	    \begin{itemize}
	        \item Basic modelling ready: simple roads (multi-lane) with different physical (and mental) properties of objects
	        \item Basic tooling support: setting up testbed parameters, map, parameters of active objects
	        \item Basic measurements ready: log output, throughput measurements, ability to save sim runs for future inspection
	        \item Basic GUI ready: able to display animations either from live simulation or saved as a file
	    \end{itemize}

	    \item by March 25th - end of project development (+buffer). Could go in one or some of the directions:
	    \begin{itemize}
	        \item Larger size of the model: graph with many connections
	        \item Loading map data from actual OpenStreetMap sources (filtering highways, counting lanes, etc.)
	        \item Attempting in-model traffic lights and model parameters optimization with different algorithms
	        \item Something else here gentlemen?
	    \end{itemize}

	    \item by 1st of April - documentation and report
	    \begin{itemize}
	        \item Code prepared and ensured for correctness and visibility
	        \item Report ready and submitted.
	        \item Presentation ready, rehearsed
	    \end{itemize}

	\end{itemize}

	\item Things done to date
	\begin{itemize}
		\item (Should be by that moment) Basic simulation skeleton and architecture
		\item Graple deployment harness
		\item Basic log system
	\end{itemize}

\end{itemize}


\section{Project Organisation} %~40% of the report
Describe how you will work together as a team. You should set out the roles you expect team members to play and what
processes and tools you will use to collaborate together as a team. You should also explain the process you expect to
use for handling peer assessment as well as the mechanisms you have agreed upon for handling any conflicts within the
team that may arise.

\begin{itemize}
	\item Teamwork
	\begin{itemize}
		\item Distribution of tasks
    	\item Conflict resolution
    	\item Efforts planned from each member
    	\item Meetings (could tie in the tools in this section?)
        \begin{enumerate}
            \item Organisation of matters to discuss
            \item Organisation of meeting time
        \end{enumerate}
        \item peer assesment (marks)

        \item Process
        \begin{itemize}
            \item Kanban-like process with board and no strict iterations defined
            \item Minimum viable product set out rather early (half-time) so should have features to add on later
            \item Git: for now master-only, will switch to features branches as everyone is comfy with git
            \item Test: obligatory automated unit-testing for components and features
            \item Peer review: post-commit review of features (peer). At least 1 person should have looked at code after commit.
        \end{itemize}
	\end{itemize}

	\item Tools
	\begin{itemize}
		\item Trello
		\item HipChat (inc. Git commit \& trello plugin)
	    \item JetBrain's IntelliJ Idea IDE for everyone
	    \item PlantUML for UML diagrams?
	\end{itemize}

\end{itemize}



